\documentclass[11pt]{article}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{graphicx}
%\usepackage{url}
\usepackage{relsize} % provides \relscale, \larger, etc. to be used *in the document*
\usepackage{color}
\XeTeXdashbreakstate=1 % Tell XeLaTeX it's OK to break lines after em-dashes.
\newcommand{\SetFont}[1]{\setmainfont[Ligatures=TeX]{#1}} % preferred to "Mapping=tex-text"
\newcommand{\UseGaramond}[1]{%
	\usepackage[urw-garamond]{mathdesign}  % goes before fontenc, fontspec, etc.
	\usepackage[T1]{fontenc}
	\usepackage{fontspec,xltxtra,xunicode}
	\SetFont{#1}}
%\UseGaramond{EB Garamond}\newcommand{\myparagraph}[1]{\paragraph{\sc #1}}\newcommand{\myfontscale}{\relscale{1.00}}
\UseGaramond{GaramondNo8}\newcommand{\myparagraph}[1]{\paragraph{#1}}\newcommand{\myfontscale}{\relscale{1.00}}
\usepackage[letterpaper,left=1.25in,right=1.25in,top=0.90in,bottom=0.90in]{geometry}
%\renewcommand{\baselinestretch}{1.66}\normalsize % doublespace
\renewcommand{\baselinestretch}{1.17}\normalsize % e.g. 12 on 14
%\renewcommand{\baselinestretch}{1.26}\normalsize % e.g. 13 on 15
\setlength{\parindent}{0in}  % Don't indent paragraphs
\setlength{\parskip}{2.5ex}    % Add space between paragraphs
\newcommand{\ie}{i.e.\@\xspace}
\newcommand{\eg}{e.g.\@\xspace}
\newcommand{\cf}{cf.\@\xspace}
\newcommand{\etc}{etc.\@\xspace}
\newcommand{\viz}{viz.\@\xspace}
\newcommand{\vs}{vs.\@\xspace}
\newcommand{\pr}{\mathsf{P}} % probability
%\newcommand{\expct}{\mbox{\boldmath $\mathsf E\,$}}
%\newcommand{\expct}{\mathsf E\,}
%\newcommand{\cov}{\mathop{\rm cov}\nolimits}
%\newcommand{\var}{\mathop{\rm var}\nolimits}
%\newcommand{\var}{\sigma^2}
\newcommand{\cmnt}[1]{}
\renewcommand{\cmnt}[1]{{\color{red}[#1]}}
\newcommand{\fn}[1]{\footnote{#1}}

\author{Marshall Abrams, University of Alabama at Birmingham, mabrams@uab.edu}

\begin{document}
\pagestyle{empty}
\myfontscale % only works in document, more or less

{\Large ``popco" transmission in CultranDejanet, SuccessBias1, etc.}\\
{\large Marshall Abrams, University of Alabama at Birmingham}


Let $a$ be the activation of a node, and $a'$ be the next activation.
Then, if the incoming communication is .05, the update function
is:
\[
x' = \min(1,x + .05(1 - x)) = \min(1,.95x + .05)
\]
(A positive increment can't push the activation below the
minimum, so we can ignore that possibility.)

When the incoming communiction is -.05, the update function is:
\[
x' = 
\max(-1,x - .05(x \;\,-\;\;\; -1)) = 
\]
%
\[
\max(-1,x - .05(x + 1)) =  \max(-1, .95x - .05)
\]
%

So the general update function is
\[
.95x \pm .05
\]
with the additional constraint that values outside of [-1,1] are
mapped back to the nearest extremum.

Note that although the original formula was intended to reflect
distance of the activation from the extremum in the direction of
push, we see here that the formula reduces to one in which:
\begin{itemize}\vspace{-2ex}
\item We simply reduce the activation by 5\%, whatever the
activation was\ \ldots
\item Then add or subtract .05 (no scaling here)
\item And then reduce the result back to the extremum, if necessary.
\end{itemize}
Well, I suppose there is still a different way to think about the
process.  After all, $1-x$ times .05, where $x = -1$, is
equal to .10, whereas when $x=1$, it's 0.  This is reflected
in the fact that the result of 0.95 times $x$ differs depending
on $x$.  It's still a linear function, $ax+b$, though.

Note that when $x=1$ and the communication is .05, the effect is
$.95 + .05$, i.e. to simply leave $x$ as is.  Likewise when
$x=-1$ and the communication is -.05.  Oh---so the $\min$/$\max$
operations are not needed.  Ah---They're not needed for the above
formulas, but clipping to 1 and -1 is needed when 
{\tt min-dist-from-extremum} is not 0, since in that case the
increment will often be greater than .05, in effect.  \eg when 
{\tt min-dist-from-extremum} $=1$, the first formula above would
become $\min(1,x+.05)$ whenever $x$ was positive, so when \eg
$x=1$, $x+.05>1$.  (This also conveys how setting {\tt
min-dist-from-extremum} to a value other than 1 causes
convergence to occur more quickly, and causes departure from an extreme
to become more difficult.  \cf NodeUpdateNotes.md.)

(Note that the $.95x$ is not the same as a decay function in the
sense that's common in connectionist/neural networks, since if a
node receives no transmission, this reduction isn't applied here.  A
real decay function acts on every tick regardless of what
happens with incoming transmissions.)

%\bibliographystyle{myforthcoming} % the .bst file
%\bibliography{phil}
\end{document}

